\section{Outline of the Algorithm}
\notiz{noch 1:1 aus der MA}
We briefly outline the steps of the algorithm described in this thesis.
The goal is to constructively recognize a black box group $G$, given it is isomorphic to a wreath product $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive.
 
 
 \begin{itemize}[leftmargin=3.0cm,labelsep=0.5cm]
\item[\textbf{INPUT:}] a black-box group $G = \langle X \rangle$ encoded as bit strings of uniform
length $N$ and a real number $\epsilon$ with $0 < \epsilon < 1$.
\item[\textbf{OUTPUT:}] an isomorphism $\varphi \colon G\to A_n\wr_\Gamma H$ if $G$ is isomorphic to \mbox{$A_n\wr_\Gamma H$}
with $H\leq S_\Gamma$ transitive, else failure.
\end{itemize}
In the following description we assume that $G$ is isomorphic to a wreath product $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive.
If this is not the case, then either one of the steps will fail, or the correctness check in Step~\ref{stepcorr} will report \texttt{false}.
Further note that we repeat this sequence of steps multiple times, until we either find an isomorphism or with sufficiently high probability $G$ is not
isomorphic to a wreath product $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive.
\begin{enumerate}
\item \label{stepone}
By taking random elements of $G$, find an element $g$ such that $g^{\frac{|g|}{2}}$ is an element of the base group.
As we are in a black box situation, we can not decide whether or not an element is in the base group.
Thus we continue the computation until an error occurs.
In that case we try with the next element, unless we have tried sufficiently many times such that we can be sure with probability at least $1-\epsilon$ that $G$ is not
isomorphic to a wreath product $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive.
In Lemma~\ref{lemmapropbasered}
%Let $n\geq 6$, $G=K\wr_\Gamma H$ and $H\leq S_m$. % and $P=\{g\in G \mid 2\text{ divides } |g| \text{ and } g^{\frac{|g|}{2}} \in B\}$.
we show that for $n\geq 6$ the proportion of elements $g$ in $A_n\wr_\Gamma H$ such that $g^{\frac{|g|}{2}}$ is an element of the base group is at least $\frac{3}{8}_.$
\item With Lemma~\ref{directproductnts} we show that the only normal subgroups $A$ of the base group $B\cong A_n^\Gamma$ are isomorphic to $A_n^s$ with territory size $s$ for $0\leq s \leq |\Gamma|$.
This also yields that, given $H$ is transitive on $\Gamma$, the normal closure of an element of the base group under $A_n\wr_\Gamma H$ is equal to the base group.
Having the base group computed, we try to reduce the size of the territory by taking random elements $g$ of the current subgroup $A\cong A_n^s$
and computing the normal closure of $g^{\frac{|g|}{2}}$ under $A$.
Lemma~\ref{Rabschätzung} shows that for $n\geq 6$ and $s\geq 2$ the proportion of elements $g$ in $A_n^s$
such that $g^{\frac{|g|}{2}}$ is in $A_n^t$ for $1\leq t <s $ is at least $\frac{1}{10}\frac{1}{\sqrt n}$.
Hence we repeat this process until with sufficiently high probability we obtain a subgroup isomorphic $S$ to $A_n$ with singleton territory.
\item In Section~\ref{toprec} we show that the top group $(1_{A_n^\Gamma}, H)$ of $A_n\wr_\Gamma H$ acts on the singleton territories precisely as $H$ acts on $\Gamma$.
Thus, given a subgroup isomorphic to $A_n$ with singleton territory, we can determine a $G$-set $\Gamma'=\{S^{t_1},\dots,S^{t_m}\}$ for $t_1,\dots,t_m\in G$.
By the transitivity of $H$ this set is in bijection to $\Gamma$.
This way we can identify the top element of any $g\in G$.
\item \label{recstep}
We use the recognition algorithm by Jambor et al. $2013$ \cite{jambor2013fast} to check if $S$ is isomorphic to an alternating group of degree $n\geq 9$ and determine $n$.
If this is not the case we start from Step~\ref{stepone} again.
As shown in Section~\ref{recbase}, we can use the results of the algorithm by Jambor et al. %to fully identify any element of the wreath product, given we have identified the top element before.
to construct a map $\varphi$ from $G$ to $A_n \wr_\Gamma S_\Gamma$.
If indeed $G$ is isomorphic to $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive and $S\cong A_n$ is a single component subgroup, then $\varphi$ is an isomorphism which we proceed to check in the next step.
\item \label{stepcorr}
\begin{sloppypar}
As a last step we perform a correctness check and for now assume that we are uncertain, whether or not $G$ is isomorphic to a wreath product $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive.
For this check we first compute the centralizer $C$ in $G$ of a "diagonal subgroup" \mbox{$D^*=\{s^{t_1}\dots s^{t_m}\mid s\in S\}$}, as described in Section~\ref{comptop}.
We check whether for all $i\in \{1,\dots, m\}$ and $c\in C$ there is a $j\in \{1,\dots, m\}$ such that \mbox{$(s^{t_i})^c=s^{t_j}$} \fa $s \in S$.
If that is the case, then $C$ acts on $\Gamma'$ by Lemma~\ref{lemabove} and by Corollary~\ref{corabove} we have $(\langle Y\rangle)\varphi = A_n\wr_{\Gamma'} C^{\Gamma'}$ for $\langle S^{t_1}, \dots , S^{t_m}, C\rangle =\langle Y\rangle$.
Further we compute the centralizer of $\langle S^{t_1}, \dots , S^{t_m} \rangle$ in $C$ and check if it is trivial, which is precisely the case when $C$ acts faithfully on $\Gamma'$ by
Lemma~\ref{lemmatreu}.
In this case $\varphi$ is an isomorphism from $\langle Y \rangle$ to $A_n\wr_{\Gamma'} C^{\Gamma'}$.
% Note that, given $G$ is isomorphic to $A_n \wr_\Gamma H$, then $C$ is the top group of 
% If $G$ is indeed isomorphic to $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive and our probabilistic computations up to this point are correct, then $C$ is isomorphic to
% the top group $(1_{A_n^\Gamma}, H)$ and $\langle S^{t_1},\dots, S^{t_m}\rangle$ is isomorphic to the base group $(K^\Gamma,1_H)$.
% Using $C$ and $S^{t_1},\dots, S^{t_m}$, we try to construct generators $X$ such that the map $\varphi$ computed in Step~\ref{recstep} induces an isomorphism 
% from $\langle X \rangle$ to $A_n \wr_\Gamma H$ for some $H\leq S_\Gamma$.
Hence we found an isomorphism from $G$ to $A_n\wr_{\Gamma'} C^{\Gamma'}$, precisely if $\langle Y \rangle=G$.
Thus, for each generator $g$ of $G$ we compute the image under $\varphi$ and compute the unique preimage in $\langle Y \rangle$ of $(g)\varphi$ under $\varphi$,
which we can do efficiently, as shown in Sections~\ref{sectioncomprebase} and \ref{sectiontoppreimage}.
If all generators of $G$ equal their respective preimage, then $Y$ generates $G$, which means $\varphi$ passes the correctness test and we return \texttt{true} together with the isomorphism $\varphi$.
Note that, if $G$ is isomorphic to $A_n \wr_\Gamma H$ with $H\leq S_\Gamma$ transitive and $S\cong A_n$ is a single component subgroup, then $\varphi$ is an isomorphism and $S$ and $\varphi$ pass the correctness check.
\end{sloppypar}

% Either way, if the centralizer computation suceeded, then $\langle S^{t_1},\dots, S^{t_m},C\rangle$ forms a wreath product isomorphic $S\wr_{\Gamma'} C$ by Lemma~\ref{corabove} and the
% 
\end{enumerate}
